\Title

### 2020-11-10 manuscript/manuscript.tex
Minor improvements to manuscript

\noindent following the same method described on Section
\ref{sec:eql-inversion}.
Because the $\mathbf{A}_k$ matrices have only $N \times M_k$ elements,
adjusting the size of the overlapping windows can help in reducing the computer
memory needed to fit the source coefficients and ultimately to interpolate the
observed data.
Nevertheless, in case we have too many data points that make the $\mathbf{A}_k$
matrices large enough that they cannot be stored in memory, we can apply one
more simplification on the fitting process: ignore the effect of the sources on
the $k$-th window on any observation point that falls outside it.

@@

\noindent where $\tilde{\mathbf{r}}_{k-1}$ is the residue vector containing
only the elements that correspond to the $\{\mathbf{p}_n\}_{n=1}^{N_k}$
observation points that fall under the $k$-th window; and
$\tilde{\mathbf{A}}_k$ is the Jacobian matrix between the observation points
and sources that fall under the same window.
Because the $\tilde{\mathbf{A}}_k$ matrices will have $N_k \times M_k$
elements, the computer memory needed for fitting the $\mathbf{c}_k$
coefficients is greatly reduced.

Once the $\mathbf{c}_k$ coefficients are fitted following the same method
described on Section \ref{sec:eql-inversion}, , we need to obtain the value
of the step-size parameter $\alpha_k$.
This can be achieved by minimizing the norm of the difference between the
previous residue $\mathbf{r}_{k-1}$ and the effect of the $k$-th set of
equivalent sources on every observation point:

@@

Once both the $\alpha_k$ parameter and the $\mathbf{c}_k$ coefficients are
fitted, equation \ref{eq:residue} is applied to update the residue: compute the
effect of the sources belonging to the $k$-th window on every observation
point. Worth noting that when calculating the effect of any number of sources
we don't need to pre-compute the entire Jacobian matrix: we can compute the
effect of the sources on each observation point by a simple addition of terms,
what means computing each Jacobian element at once when needed.

>>>>

\noindent following the same method described on Section
\ref{sec:eql-inversion}.
Because the $\mathbf{A}_k$ matrices have only $N \times M_k$ elements,
adjusting the size of the overlapping windows can help in reducing the computer
memory needed to fit the source coefficients.
Nevertheless, in case we have too many data points that make the $\mathbf{A}_k$
matrices large enough that they cannot be stored in memory, we can apply one
more simplification on the fitting process: ignore the effect of the $k$-th
sources on any observation point that falls outside the $k$-th window.

@@

\noindent where $\tilde{\mathbf{r}}_{k-1}$ is the residue vector containing
only the elements that correspond to the $\{\mathbf{p}_n\}_{n=1}^{N_k}$
observation points that fall under the $k$-th window; and
$\tilde{\mathbf{A}}_k$ is the Jacobian matrix between these observation points
and the $k$-th sources.
Because the $\tilde{\mathbf{A}}_k$ matrices will have $N_k \times M_k$
elements, the computer memory needed for fitting the $\mathbf{c}_k$
coefficients is greatly reduced.

Once the $\mathbf{c}_k$ coefficients are fitted following the same method
described on Section \ref{sec:eql-inversion}, we need to obtain the value
of the step-size parameter $\alpha_k$.
This can be achieved by minimizing the norm of the difference between the
previous residue $\mathbf{r}_{k-1}$ and the effect of the $k$-th sources on
every observation point:

@@

Once both the $\alpha_k$ parameter and the $\mathbf{c}_k$ coefficients are
fitted, equation \ref{eq:residue} is applied to update the residue: compute the
effect of the sources belonging to the $k$-th window on every observation
point. Worth noting that when calculating the effect of any number of sources
we don't need to pre-compute the entire Jacobian matrix: we can calculate the
effect of the sources on each observation point by a simple addition of terms,
what means computing each Jacobian element at once when needed.
